\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[rgb]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


% Font options
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Atin Sharma} \\ \vspace{1pt}
    \small Agra, India $|$ \href{mailto:atinsharma24@gmail.com}{atinsharma24@gmail.com} $|$ +91 82185 02886 \\
    \small \href{https://linkedin.com/in/atinsharma24}{linkedin.com/in/atinsharma24} $|$ \href{https://github.com/atinsharma24}{github.com/atinsharma24}
\end{center}

\section{Profile}
\vspace{2pt}
\small{Backend Engineer specializing in AI-driven data systems, RAG pipeline architecture, and high-performance API development. Expert in Python (Django/FastAPI) and Node.js for building secure, scalable AI backends with advanced retrieval logic and semantic search. Experienced in optimizing database queries and managing large-scale vector embeddings for document intelligence and business automation.}
\vspace{-4pt}
\resumeItemListStart
    \resumeItem{Production RAG Pipeline: Achieved sub-800ms retrieval across multi-format corpora using pgvector and Groq.}
    \resumeItem{WhatsApp AI Lifecycle: Managed full-cycle message orchestration from webhook ingestion to LLM response delivery.}
    \resumeItem{Async Document Ingestion: Implemented robust retry logic and status tracking for production-grade rate limit handling.}
\resumeItemListEnd\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {OpenBiz Software India Pvt Ltd}{Jul 2025 -- Mar 2026}
      {Founding Engineer}{Remote/Bangalore}
      \resumeItemListStart
        \resumeItem{Architected the zero-to-one core MERN platform, implementing strict TypeScript practices across the stack to build a scalable, production-ready foundation.}
        \resumeItem{Architected VyaparGPT, a WhatsApp-native AI assistant for Indian SMBs, successfully deploying the MVP to an initial closed-pilot cohort of $\sim$40 businesses; handled webhook ingestion $\rightarrow$ LLM orchestration $\rightarrow$ response delivery with provider fallback and session-aware context.}
        \resumeItem{Built an AI document verification module using Google Gemini API, automating data extraction from unstructured SMB documents and replacing a manual review step.}
        \resumeItem{Diagnosed and resolved N+1 query patterns in Supabase (PostgreSQL), reducing API latency by 40\% across critical endpoints through indexing and response caching.}
        \resumeItem{Engineered a fault-tolerant Razorpay subscription billing system with idempotent webhook validation, achieving 100\% payment-state consistency and reducing manual reconciliation to zero.}
        \resumeItem{Owned CI/CD pipeline setup using GitHub Actions and Vercel, reducing deployment cycle time by 30\% and eliminating environment-drift bugs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Nimbus --- AI RAG Workspace} $|$ \href{https://github.com/atinsharma24/nimbus}{\underline{github.com/atinsharma24/nimbus}}}{In Development 2026}
          \resumeItemListStart
            \resumeItem{\emph{Stack: Next.js, pgvector, Groq, Prisma}}
            \resumeItem{Architected a production RAG pipeline (pgvector + Groq API) achieving sub-800ms semantic retrieval over multi-format document corpora with streaming LLM responses.}
            \resumeItem{Designed a provider-agnostic LLM layer supporting Groq, OpenAI, and Anthropic, enabling one-config switching without downstream changes to retrieval logic.}
            \resumeItem{Implemented async ingestion with 429 retry logic and per-document status tracking for production-grade rate limit handling.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Autonomous Web Agent} $|$ \href{https://github.com/atinsharma24/autonomous-web-agent}{\underline{github.com/atinsharma24/auto-agent}}}{}
          \resumeItemListStart
            \resumeItem{\emph{Stack: OpenClaw, BrowserOS (MCP), Python, Groq}}
            \resumeItem{Designed a Claude 3.5 Sonnet + MCP orchestration layer that translates structured local context schemas into DOM-level form interactions for multi-step web workflows across dynamic web forms.}
            \resumeItem{Built a decoupled system with a lightweight Groq-based "Watcher" for cost-efficient parsing and a heavy "Executor" agent for complex interactions.}
            \resumeItem{Engineered resilient infra with local queue management and WAF/Captcha detection with graceful human-escalation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Automated Content Intelligence Pipeline} $|$ \href{https://github.com/atinsharma24/content-pipeline}{\underline{github.com/atinsharma24/pipeline}}}{}
          \resumeItemListStart
            \resumeItem{\emph{Stack: React 19, TypeScript, Node.js, OpenAI}}
            \resumeItem{Built an autonomous content pipeline running Puppeteer scraping and dual-model AI rewriting with Gemini and OpenAI failover.}
            \resumeItem{Developed a React 19 frontend with a split-screen diff view for real-time editorial comparison of AI-rewritten content.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Focus Stack:}{ Python, FastAPI, Django, Node.js, PostgreSQL, pgvector, ChromaDB, OpenAI, LangChain, Redis. } \\ 
     \textbf{Languages:}{ JavaScript/TypeScript, Python, SQL, Java} \\
     \textbf{Frontend:}{ React (v18/19), Next.js, React Native, Redux Toolkit, TailwindCSS} \\
     \textbf{Backend/DB:}{ Node.js, Express, NestJS, Django, PostgreSQL, MongoDB, pgvector, ChromaDB} \\
     \textbf{AI/LLM:}{ OpenAI, Google Gemini, Groq API, RAG Pipelines, LangChain.js, Sentence Transformers, Prompt Engineering} \\
     \textbf{DevOps:}{ Docker, GitHub Actions, Vercel, AWS (S3, DynamoDB)} \\
     \textbf{Tools:}{ Git, Postman, Socket.IO, Razorpay SDK, VideoSDK, Puppeteer}
    }}
 \end{itemize}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Expected Graduation: May 2026}
      {B.Tech in Computer Science and Engineering}{Vellore}
      \resumeItemListStart
        \resumeItem{Focus on Full Stack Development and AI Systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}