\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[rgb]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


% Font options
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Atin Sharma} \\ \vspace{1pt}
    \small Agra, India $|$ \href{mailto:atinsharma24@gmail.com}{atinsharma24@gmail.com} $|$ +91 82185 02886 \\
    \small \href{https://linkedin.com/in/atinsharma24}{linkedin.com/in/atinsharma24} $|$ \href{https://github.com/atinsharma24}{github.com/atinsharma24}
\end{center}

\section{Profile}
\vspace{2pt}
\small{Specialized Generative AI Engineer focused on LLM orchestration, agentic workflows, and high-fidelity RAG pipelines. Expert in prompt engineering, dual-model failover architectures (Gemini + OpenAI), and semantic search optimization using pgvector and ChromaDB. Experienced in designing resilient AI infrastructures with sub-800ms retrieval times and fault-tolerant message lifecycles.}
\vspace{-4pt}
\resumeItemListStart
    \resumeItem{Architected Nimbus AI: production RAG workspace with provider-agnostic LLM layer + async ingestion.}
    \resumeItem{Built Autonomous Web Agent: Claude 3.5 Sonnet + MCP orchestration for DOM-level form interaction.}
    \resumeItem{Content Intelligence Pipeline: Gemini $\rightarrow$ OpenAI dual-model rewriting + React 19 Diff View.}
\resumeItemListEnd\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {OpenBiz Software India Pvt Ltd}{Jun 2025 -- May 2026}
      {Founding Engineer}{Remote / Bangalore}
      \resumeItemListStart
        \resumeItem{VyaparGPT: HMAC-SHA256 webhook $\rightarrow$ session context $\rightarrow$ LLM dispatch $\rightarrow$ delivery; 40+ SMBs pilot, 1,000+ platform users; multi-turn context via \texttt{conversation\_history[]}.}
        \resumeItem{LLM fallback (OpenAI $\rightarrow$ Gemini on 5xx/429/timeout); Gemini Vision extracted GST, amounts, dates from WhatsApp SMB photographs, eliminating manual onboarding data entry.}
        \resumeItem{N+1 fix (JOIN rewrites, composite indexes, TTL cache) --- \textbf{40\% API latency reduction} at 1,000+ user scale.}
        \resumeItem{Razorpay: HMAC webhook validation + re-entrant idempotency check --- \textbf{100\% payment-state consistency}.}
        \resumeItem{CI/CD (GitHub Actions + Vercel): automated testing per PR, staging on merge, prod behind approval --- \textbf{30\% faster deployments}, zero broken-build incidents over four months.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Nimbus --- AI RAG Workspace} $|$ \emph{Next.js 14, TypeScript, PostgreSQL, pgvector, Prisma, Groq API, OpenAI}}{In Development 2026}
          \resumeItemListStart
            \resumeItem{Async queue ingestion (pending $\rightarrow$ indexed) with overlap chunking; pgvector cosine search for hybrid SQL + semantic filtering --- sub-800ms retrieval.}
            \resumeItem{Provider-agnostic LLM layer (\texttt{groq|openai|anthropic} config flag) + SSE streaming via Groq; 429 retry (exp. backoff) and per-document status tracking.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{DocGPT --- RAG Document Assistant} $|$ \emph{React 19, Python (Django), ChromaDB, OpenAI, Docker}}{}
          \resumeItemListStart
            \resumeItem{Django RAG pipeline: PyPDF2 overlap chunking, local all-MiniLM-L6-v2 embeddings (offline, zero API cost), ChromaDB cosine retrieval, GPT-4o-mini generation; Dockerized.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Autonomous Web Agent} $|$ \href{https://github.com/atinsharma24/auto-agent}{\underline{github.com/atinsharma24/auto-agent}} $|$ \emph{Python, Groq, BrowserOS (MCP), Claude 3.5 Sonnet}}{}
          \resumeItemListStart
            \resumeItem{Dual-agent: Claude 3.5 Sonnet Executor (DOM + form reasoning) + Groq Watcher (page-state validation between transitions).}
            \resumeItem{MCP via BrowserOS for structured DOM access; persistent queue (pending $\rightarrow$ applied/failed) with URL dedup and WAF/CAPTCHA detection.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Automated Content Intelligence Pipeline} $|$ \emph{React 19, TypeScript, Laravel, OpenAI, Gemini, Docker, Puppeteer}}{}
          \resumeItemListStart
            \resumeItem{Puppeteer SPA scraping; Gemini $\rightarrow$ OpenAI fallback rewriting; React 19 Diff View with per-article state machine; Dockerized microservices on GitHub Actions cron.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Focus Stack:}{ Python, LangChain, Groq API, pgvector, ChromaDB, OpenAI, Google Gemini, Prompt Engineering, Agentic Workflows.} \\
     \textbf{Languages:}{ JavaScript/TypeScript, Python, SQL, Java} \\
     \textbf{Frontend:}{ React (v18/19), Next.js, React Native, Redux Toolkit, TailwindCSS} \\
     \textbf{Backend/DB:}{ Node.js, Express, NestJS, Django, PostgreSQL, MongoDB, pgvector, ChromaDB} \\
     \textbf{AI/LLM:}{ OpenAI, Google Gemini, Groq API, RAG Pipelines, LangChain.js, Sentence Transformers, Prompt Engineering} \\
     \textbf{DevOps:}{ Docker, GitHub Actions, Vercel, AWS (S3, DynamoDB)} \\
     \textbf{Tools:}{ Git, Postman, Socket.IO, Razorpay SDK, VideoSDK, Puppeteer} \\
     \textbf{Patterns:}{ Webhook Validation (HMAC-SHA256), N+1 Optimization, Vector Similarity Search, Provider-Agnostic LLM Layers, Idempotent Events}
    }}
 \end{itemize}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Coursework Completed: Nov 2025 | Degree Conferred: May 2026}
      {B.Tech in Computer Science and Engineering}{Vellore}
      \resumeItemListStart
        \resumeItem{Focus on Full Stack Development and AI Systems.}
        \resumeItem{Research (Jan--Nov 2025): Blockchain-Based LLM + FHE for Academic Records --- FHE enables encrypted-data inference without decryption; blockchain provides credential audit trail.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}